### 2013-09-04 Tex/chapters/results.tex
Ergänzung zu Delta x

            The range \(\Delta x\) specifies the mesurements used for the
            data collapse.

>>>>

            The range \(\Delta x\) specifies a range on the \(x\)-axis of
            the plots after the collapse. Values inside this range are
            considered to judge the quality of the collapse. I.e.\ only
            the data points inside this range have to collapse on each
            other -- data points beyond do not have to. This accounts
            for the fact, that FSS is only near the critical point a good
            approximation.
